---
title: "Group No.4 Assignment 1 Company Reputation Poll"
author: Athbah Alrugibah, Alyazid Alhumaydani, Dhawi Almajnouni, Hassan AlTamimi,
  Mariam Busaleh
date: "2022-10-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidytuesdayR)
library(ggplot2)
library(DataExplorer)
library(randomcoloR)
```

## 1.Introduction

The Axios-Harris Poll 100 is a trusted raking of the reputation of the
companies most on the minds of Americans using a framework Harris has
used since 1999.<http://theharrispoll.com/partners/media/axios-harrispoll-100/>

## 2.Dataset
**• Title:** 2022 Corporate Reputation and poll Rankings

**• Year:** 2022

**• Source:** Thomas Mock (2022). Tidy Tuesday: A weekly data project aimed at the R ecosystem. <https://github.com/rfordatascience/tidytuesday.>

**• Purpose of Dataset:** A great dataset for beginners who is learning to work in data analysis and visualization.

**• Content:** Reputation:company,industry,name,score,rank;poll: company	industry	2022_rank	2022_rq	change	year	rank	rq

**• Structure:** Mainly consist of integers, floating point values also string

**• Summary:** This dataset describes attributes of the Reputation and poll of Companies so the dataset can be make used to propose exploratory data analysis.

## 3.Problem Statement 

## 4.Objective

## 5.EDA

**Download all data files**

```{r, echo=FALSE}
#tuesdata <- tidytuesdayR::tt_load('2022-05-31')
poll <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-05-31/poll.csv')
reputation <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-05-31/reputation.csv')
```

**Individual data frames**

```{r, echo=FALSE}
#poll <- tuesdata$poll
#reputation <- tuesdata$reputation

poll
reputation

```

**# Cleaning data (removes unwanted columns and NA entries )**

```{r, echo=FALSE}
 poll %>%
  select(company,industry,year,rq) %>%
  na.omit() -> poll

reputation %>%
  select(company,industry,name,score) -> reputation
poll
reputation
 
```

**# Overall Reputation score and RQ for each company **

```{r, echo=FALSE}
  aggregate(reputation$score, list(reputation$company,
                                 reputation$industry), FUN=mean) -> rep_overall
c("company", "industry", "average_score") -> colnames(rep_overall)

aggregate(poll$rq, list(poll$company,
                        poll$industry), FUN=mean) -> poll_overall
 c("company", "industry", "average_rq") -> colnames(poll_overall)
 poll_overall
```

**# Merging both data sets**

```{r, echo=FALSE}
total <- merge(poll_overall,rep_overall,by=c("company","industry"))
total  
```
## Plot

**# Creating Color Palette**

```{r, echo=FALSE}
n <- 20
palette <- distinctColorPalette(n)
```

**# Plotting Overall Reputation, Poll, and their total**

```{r, echo=FALSE}
ggplot(rep_overall, aes(average_score, industry)) +
  ggtitle("Industries' Reputation Scores") +
  geom_point()

ggplot(poll, aes(rq, industry)) + 
  ggtitle("Industries' RQ") +
  geom_point()

ggplot(total, aes(average_rq, average_score, colour = industry)) +
  ggtitle("RQ vs Reputation Score of Each Industry")+
  geom_point() +
  scale_color_manual(values = palette)
```

**#Hypothesis Testing**

**#Overall Reputation hypothesis testing. The null hypothesis is groceries don't have a higher overall reputation than other industries**

```{r, echo=FALSE}
rep_overall[rep_overall$industry == "Groceries", ] -> rep_groceries

rep_x <- mean(rep_groceries$average_score)
rep_y <- mean(rep_overall$average_score) 
rep_sd <- sd(rep_overall$average_score) 
rep_n <- nrow(rep_groceries)
(rep_x-rep_y)/(rep_sd/sqrt(rep_n)) -> rep_z

if (rep_z > qnorm(p=.05, lower.tail=FALSE)) {
  print("We reject the null hypothesis at the 5% significance level. The grocery industry does have a higher overall reputation than other industries")
} else {
  print("We fail to reject the null hypothesis at the 5% significance level. The grocery industry doesn't have a higher overall reputation than other industries")
}  
```

**#Poll hypothesis testing, The null hypothesis is groceries don't have a higher RQ than other industries**

```{r, echo=FALSE}
poll[poll$industry == "Groceries", ] -> poll_groceries

poll_x <- mean(poll_groceries$rq)
poll_y <- mean(poll$rq)
poll_sd <- sd(poll$rq)
poll_n <- nrow(poll_groceries)
(poll_x-poll_y)/(poll_sd/sqrt(poll_n)) -> poll_z

if (poll_z > qnorm(p=.05, lower.tail=FALSE)) {
  print("We reject the null hypothesis at the 5% significance level. The grocery industry does have a higher rq than other industries")
} else {
  print("We fail to reject the null hypothesis at the 5% significance level. The grocery industry doesn't have a higher rq than other industries")
}  
```
